[dcpo_demsupport]

### 2020-07-30 paper/dcpo_demsupport.Rmd
fix df_controls encoding issue; fix for painful change in v2.0 as_tibble behavior

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: svm-latex-ms2.tex
title: "[dcpo_demsupport]"
thanks: "Corresponding author: [yuehong-tai@uiowa.edu](mailto:yuehong-tai@uiowa.edu). Current version: `r format(Sys.time(), '%B %d, %Y')`."
author:
- name: Yuehong 'Cassandra' Tai
  affiliation: University of Iowa
- name: Yue Hu
  affiliation: Tsinghua University
- name: Frederick Solt
  affiliation: University of Iowa
abstract: "Public opinion’s effect on democratic institutions is important and long-studied topic.  Claassen (2020) renewed attention to this question by using a Bayesian latent variable approach to measure mass democratic support from survey data and concluded such support has a positive effect on subsequent democratic change and especially on democracy’s endurance once in place.  In this article, we reexamine the question, bringing more survey data on democratic support; a superior measure, Dynamic Comparative Public Opinion (DCPO); and an improved methodological approach that takes the uncertainty in this measure into account.  Our results [further reinforce/contradict] the long-held view that democracies depend on public support to survive."
keywords: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
spacing: double
bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), ".bib$", recursive = TRUE))`}
# csl: https://raw.githubusercontent.com/citation-style-language/styles/master/american-political-science-association.csl
biblio-style: apsr
citecolor: black
linkcolor: black
endnote: no
header-includes:
      - \usepackage{array}
      - \usepackage{caption}
      - \usepackage{graphicx}
      - \usepackage{siunitx}
      - \usepackage{colortbl}
      - \usepackage{multirow}
      - \usepackage{hhline}
      - \usepackage{calc}
      - \usepackage{tabularx}
      - \usepackage{threeparttable}
      - \usepackage{wrapfig}
nocite: |
  @Solt2020a
---

@@

ls_year <- 1988:2017
ls_country <- dcpo_input$data$country %>% 
  unique

df_controls <- read_csv(here::here("data", "control_variables.csv"),
                        col_types = cols(
                          .default = col_double(),
                          Country = col_character(),
                          Cnt_code = col_character(),
                          ISO_code = col_character(),
                          Region_UN = col_character()))

first_year <- min(dcpo_input$data$year)

df_theta <- purrr::map(1:1000, function(anEntry) {
  dcpo_theta$theta[anEntry,,] %>% 
    as_tibble() %>% 
    rename_with(~ ls_country, .cols = starts_with("V")) %>% 
    mutate(year = first_year + row_number() - 1) %>% 
    pivot_longer(cols = ls_country,
                 names_to = "country",
                 values_to = "theta") %>%
    arrange(country, year) %>% 
    left_join(df_controls, by = c("country", "year")) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

>>>>

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: svm-latex-ms2.tex
title: "[dcpo_demsupport]"
thanks: "The authors contributed equally to this work.  Corresponding author: [yuehong-tai@uiowa.edu](mailto:yuehong-tai@uiowa.edu).  Current version: `r format(Sys.time(), '%B %d, %Y')`."
author:
- name: Yuehong 'Cassandra' Tai
  affiliation: University of Iowa
- name: Yue Hu
  affiliation: Tsinghua University
- name: Frederick Solt
  affiliation: University of Iowa
abstract: "Public opinion’s effect on democratic institutions is important and long-studied topic.  Claassen (2020) renewed attention to this question by using a Bayesian latent variable approach to measure mass democratic support from survey data and concluded such support has a positive effect on subsequent democratic change and especially on democracy’s endurance once in place.  In this article, we reexamine the question, bringing more survey data on democratic support; a superior measure, Dynamic Comparative Public Opinion (DCPO); and an improved methodological approach that takes the uncertainty in this measure into account.  Our results [further reinforce/contradict] the long-held view that democracies depend on public support to survive."
keywords: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
spacing: double
bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), ".bib$", recursive = TRUE))`}
# csl: https://raw.githubusercontent.com/citation-style-language/styles/master/american-political-science-association.csl
biblio-style: apsr
citecolor: black
linkcolor: black
endnote: no
header-includes:
      - \usepackage{array}
      - \usepackage{caption}
      - \usepackage{graphicx}
      - \usepackage{siunitx}
      - \usepackage{colortbl}
      - \usepackage{multirow}
      - \usepackage{hhline}
      - \usepackage{calc}
      - \usepackage{tabularx}
      - \usepackage{threeparttable}
      - \usepackage{wrapfig}
nocite: |
  @Solt2020a
---

@@

df_controls <- read_csv(here::here("data", "control_variables.csv"),
                        col_types = cols(.default = col_double(),
                                         country = col_character(),
                                         country_name = col_character(),
                                         ISO = col_character(),
                                         Region_UN = col_character(),
                                         Region_UN.1 = col_character())) %>% 
  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
         country = countrycode::countrycode(country0, "country.name", "country.name"))

ls_country <- levels(dcpo_input$data$kk)
first_year <- min(dcpo_input$data$year)

df_theta <- purrr::map(1:1000, function(anEntry) {
  dcpo_theta$theta[anEntry,,] %>% 
    as_tibble(.name_repair = ~make.names(., unique = TRUE)) %>% 
    rename_with(~ ls_country, .cols = everything()) %>% 
    mutate(year = first_year + row_number() - 1) %>% 
    pivot_longer(cols = all_of(ls_country),
                 names_to = "country",
                 values_to = "theta") %>%
    arrange(country, year) %>% 
    left_join(df_controls, by = c("country", "year")) %>% 
    plm::pdata.frame(index = c("country", "year"))
})
